\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2017-05-19 latex_compared/UMEM_CoSim_corrected.tex
corrected item d

\subsection{Coupling process} 
The coupling process of a simplified single zone
model and contextual surrounding buildings is described in previous studies
\citep{thomas2014multiscale}, which forms the basis for the methodology
in the current effort. This process utilizes the Design Performance Viewer
(DPV) and associated workflow. The DPV is a tool written to extract and
simulate an EnergyPlus input data file (IDF) from an
Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM
\citep{Schlueter2009}. The central philosophy behind the tool is a rapid simulation
of the building information model from the earliest design possible and can be
used throughout the life-cycle of the building including retrofit analysis
\citep{Miller:2014tu}. This process is achieved by augmenting the information
in the BIM with default values and abstracting information not relevant for
energy simulation. The tool already has a simplified notion of surrounding
buildings, which are modeled in the BIM as simple mass objects without further
information and are exported as shading surfaces to EnergyPlus. This
functionality is used for creating the CitySim mass scene and leads to a crude
model of the urban context of the building. The current DPV philosophy of
allowing the designer to iterate rapidly on early design decisions based on
feedback about the performance of the design remains. This approach includes
streamlining the process where running a simulation requires no effort from
the designer due to automatic creation of input files, execution, and analysis
of the results.% \noteDT{not sure the second reference includes coupling...}

@@

% \noteDT{with respect to what???}
% \noteDT{greater than what??}

@@

% \ref{fig:hpz_profiles}-\ref{fig:hit_profiles}

% \begin{figure}
% \centering
% \includegraphics[scale=0.45]{figures/HPZ_combinedclusterandcal_4}
% \caption{HPZ Heating Energy Typical Profiles}
% \label{fig:hpz_profiles}
% \end{figure}

% \begin{figure}
% \centering
% \includegraphics[scale=0.45]{figures/HPK_combinedclusterandcal_4}
% \caption{HPK Electrical Energy Typical Profiles}
% \label{fig:hpk_profiles}
% \end{figure}

% \begin{figure}
% \centering
% \includegraphics[scale=0.45]{figures/HIT_combinedclusterandcal_4}
% \caption{HIT Electrical Energy Typical Profiles}
% \label{fig:hit_profiles}
% \end{figure}

@@

% Applied with essential functions for the
% region, the building has definitely become the new landmark.

% \noteDT{move main
% sentence to start of paragraph}

\subsection{Model development}
The information required in the simulation mainly comprises three parts:
physical, geometrical and operational data. The geometry information including
the shape, dimension, structure and materials was obtained from the Real
Estate and Infrastructure Department of École Polytechnique Fédérale de
Lausanne (EPFL), which was responsible for carrying out the project from call
to tender to construction. However, since the documents provided were full of
details but also conflicting with what has been installed as compared to the
documents before construction, the task to realize a precise model of the
buildings itself is rather tedious. Besides, it is even more challenging to
get the operational data (daily occupancy, lighting, and electrical equipment
usage level and ventilation rate) as the building has only recently been set
in operation mode and as engineers and technicians have been working on
improving the controls. Therefore, due to unreliable monitoring data, the
calibration step of the model was not undertaken.\\
% \noteDT{delete:
% "unfortunately". we are cold hard scientists battling the evil nemesis that is
% entropy and his plan to suffocate everyone with the inevitable heat death of
% the universe. we have no time for lame excuses. we just abandon. no regrets.
% thug life!}

@@

% As a summary, three models are compared: a detailed EnergyPlus model, a simplified CitySim model and a simplified EnergyPlus model. In addition to what a coupled simplified CitySim and EnergyPlus model is realized and its results analyzed with respect to the other three models.

% \section{Results}
% {\color{red}Here we show all of the data of the comparison between the simulation outputs and the measured data from the campus}

% \section{Results}
\subsection{Comparison of EnergyPlus and CitySim}

Both the CitySim and EnergyPlus engines are utilized in this case study. The
first comparison to observe is the differences between the two engines when
focused on the Quartier Nord building. When simulated in isolation, the
CitySim engine predicts a 28.6\% increase in heating load and a 44.4\%
increase in cooling load as compared to EnergyPlus. This phenomenon is due to
the differences in the way each of these engines calculates heating and
cooling loads. Use of the co-simulation process brings the engines to within
5.4\%. Figure \ref{fig:qn_eplusvscitysim_cooling} illustrates these
differences for cooling and Figure \ref{fig:qn_eplusvscitysim_heating} for
heating.
% \noteDT{in
% the figures that follow, Cosim and CoSim are both used. decide. then stick to
% one spelling. everywhere. notice how i need a break? tgif!}

% as closely as possible\noteDT{??! aligned as closely as
% possible? this is not how we overcome the dark lord. can we quantify this?}

% ,\noteDT % {comma-comma-comma, or not}

@@

\subsection{EnergyPlus co-simulation results}
The Quartier Nord building is also simulated within the solo and
cosimulation environments. When
focusing on the EnergyPlus results, a 7.5\% decrease in cooling energy is
observed, as seen in Figure
\ref{fig:qn_eplus_cosimvssolo_cooling}. A 2.8\% increase in heating energy is
observed, as seen in Figure
\ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less pronounced
than the HPI and theoretical case studies due to the number and proximity of
surrounding buildings is not as large. Long wave radiation exchange in this situation 
doesn't have as large of an impact on the heating and cooling calculations.
% \noteCM{I'm planning to elaborate on
% these sections
% but am struggling to interpret the results other than just "co-sim and solo
% are different" -- what do you guys think?}\noteDT{well, for a start, the two
% case studies differ in the amount of LWR radiation. we could quantify that?
% also, the number of surfaces of the e+ model with viewfactor to surrounding
% buildings?}

@@

@@

\subsection{Acknowledgements}
The authors would like to acknowledge the ETH Z\"urich Campus Facilities
Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
Thoma for their assistance in this project. This research was funded by the
Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
Energy Modeling (UMEM) project. 
% The authors would also like to acknowledge
 % Emanuel Thoma for his work in developing the geometric models.% %
 % \noteDT{We also
% want to acknowledge Emanuel Thoma for his work on the Hoenggerberg model, no?}

>>>>

\subsection{Coupling process} 
The coupling process of a simplified single zone
model and contextual surrounding buildings is described in previous studies
\citep{thomas2014multiscale}, which forms the basis for the methodology
in the current effort. This process utilizes the Design Performance Viewer
(DPV) and associated workflow. The DPV is a tool written to extract and
simulate an EnergyPlus input data file (IDF) from an
Autodesk\textsuperscript{TM} Revit\textsuperscript{TM} BIM
\citep{Schlueter2009}. The central philosophy behind the tool is a rapid simulation
of the building information model from the earliest design possible that can be
used throughout the life-cycle of the building including retrofit analysis
\citep{Miller:2014tu}. This process is achieved by augmenting the information
in the BIM with default values and abstracting information not relevant for
energy simulation. The tool already has a simplified notion of surrounding
buildings, which are modeled in the BIM as simple mass objects without further
information and are exported as shading surfaces to EnergyPlus. This
functionality is used for creating the CitySim mass scene and leads to a crude
model of the urban context of the building. The current DPV philosophy of
allowing the designer to iterate rapidly on early design decisions based on
feedback about the performance of the design remains. This approach includes
streamlining the process where running a simulation requires no effort from
the designer due to automatic creation of input files, execution, and analysis
of the results.% \noteDT{not sure the second reference includes coupling...}

@@

@@

@@

\subsection{Model development}
The information required in the simulation mainly comprises three parts:
physical, geometrical and operational data. The geometry information including
the shape, dimension, structure and materials was obtained from the Real
Estate and Infrastructure Department of École Polytechnique Fédérale de
Lausanne (EPFL), which was responsible for carrying out the project from call
to tender to construction. However, since the documents provided were full of
details but also conflicting with what has been installed as compared to the
documents before construction, the task to realize a precise model of the
buildings itself is rather tedious. Besides, it is even more challenging to
get the operational data (daily occupancy, lighting, and electrical equipment
usage level and ventilation rate) as the building has only recently been set
in operation mode and as engineers and technicians have been working on
improving the controls. Therefore, due to unreliable monitoring data, the
calibration step of the model was not undertaken.\\

@@

\subsection{Comparison of EnergyPlus and CitySim}

Both the CitySim and EnergyPlus engines are utilized in this case study. The
first comparison to observe is the differences between the two engines when
focused on the Quartier Nord building. When simulated in isolation, the
CitySim engine predicts a 28.6\% increase in heating load and a 44.4\%
increase in cooling load as compared to EnergyPlus. This phenomenon is due to
the differences in the way each of these engines calculates heating and
cooling loads. Use of the co-simulation process brings the engines to within
5.4\%. Figure \ref{fig:qn_eplusvscitysim_cooling} illustrates these
differences for cooling and Figure \ref{fig:qn_eplusvscitysim_heating} for
heating.

@@

\subsection{EnergyPlus co-simulation results}
The Quartier Nord building is also simulated within the solo and
cosimulation environments. When
focusing on the EnergyPlus results, a 7.5\% decrease in cooling energy is
observed, as seen in Figure
\ref{fig:qn_eplus_cosimvssolo_cooling}. A 2.8\% increase in heating energy is
observed, as seen in Figure
\ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less pronounced
than the HPI and theoretical case studies due to the number and proximity of
surrounding buildings is not as large. Long wave radiation exchange in this situation 
doesn't have as large of an impact on the heating and cooling calculations.

@@

\section{Discussion}
Two campus case studies were presented in this paper to showcase a novel process of extracting 
model meta-data, conversion of those data into models for two separate simulation engines, and the solo
and co-simulation process of those engines on two real-world case studies. This section will outline 
the advantages and disadvantages of undertaking this process with respect to factors such as 
usability for various applications, simulation speed and resources, and an overview of the tools 
involved in the process.

Advantages of a co-simulation process between EnergyPlus and CitySim were uncovered through
this study. The key advantage is that each of the engines is enabled to account for various 
physical phenomenon in their simulation process that were previously impossible. For example, 
through co-simulation, EnergyPlus was able to utilize the long wave radiation exchange capabilities 
of CitySim. \noteCM{Here we continue the discussion of advantages}

Disadvantages of the co-simulation process are mainly centered upon the increase
in computing time and power needed for the FMI to coordinate data exchange between 
the two simulation engines. \noteCM{Here we continue the discussion of disadvantages}

@@

\subsection{Acknowledgments}
The authors would like to acknowledge the ETH Z\"urich Campus Facilities
Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
Thoma for their assistance in this project. This research was funded by the
Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
Energy Modeling (UMEM) project. 
% The authors would also like to acknowledge
 % Emanuel Thoma for his work in developing the geometric models.% %
 % \noteDT{We also
% want to acknowledge Emanuel Thoma for his work on the Hoenggerberg model, no?}

### 2017-05-19 latex_corrected/UMEM_CoSim.tex
updated figure 3 (removed dotted lines - they really don't make much sense)
corrected item d

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables
\usepackage{lmodern}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{lineno}
\RequirePackage{fix-cm}

@@

The CitySim simulation engine is an example of such a program designed and
optimized for urban-scale simulation. CitySim is an urban performance
simulation engine that comprises a solver module as well as a graphical user
interface. It focuses on the energy flows of multiple simplified building
models and their interdependent relationship with their urban climate
\citep{Robinson:2009tm}. CitySim includes building thermal, urban radiation,
occupant behavior, and plant/equipment models integrated as a single
simulation engine. CitySim simulates multiple buildings up to city scale using
simplified models to achieve a good compromise between modeling
accuracy, computational overheads, and data availability. Each building's
thermal behavior is based on an electrical analogy using a two node resistor-
capacitor network. The internal lighting, people, and miscellaneous loads are
modeled using a simplified occupancy-based approximation. The heating,
ventilation, and air-conditioning (HVAC) systems are modeled using a single
equation that approximates the total mass flow rate required to meet the
sensible and latent loads of each building as a whole. Each of these
simplifying approximations empowers the urban-scale simulation to have
reasonable execution times on the number of buildings being
simulated.

>>>>

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables
\usepackage{lmodern}
\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{lineno}
\usepackage{tikz}
\RequirePackage{fix-cm}

@@

The CitySim simulation engine is an example of such a program designed and
optimized for urban-scale simulation. CitySim is an urban performance
simulation engine that comprises a solver module as well as a graphical user
interface. It focuses on the energy flows of multiple simplified building
models and their interdependent relationship with their urban climate
\citep{Robinson:2009tm}. CitySim includes building thermal, urban radiation,
occupant behavior, and plant/equipment models integrated as a single
simulation engine. CitySim simulates multiple buildings up to city scale using
simplified models to achieve a good compromise between modeling
accuracy, computational overheads, and data availability. Each building's
thermal behavior is based on an electrical analogy using a two node resistor-
capacitor network. The internal lighting, people, and miscellaneous loads are
modeled using a simplified occupancy-based approximation. The heating,
ventilation, and air-conditioning (HVAC) systems are modeled using a
set of equations that approximates the total mass flow rate required to meet the
sensible and latent loads of each building as a whole. Each of these
simplifying approximations empowers the urban-scale simulation to have
reasonable execution times on the number of buildings being
simulated.
